### 2013-02-14 doc/icml2013/evaluation.tex
Minor fixes; printing tensor recovery error

Dataset 1: visualization ($b = 1, p = 3$) (DONE)
Plot for visualization

Dataset 2: $b = 30$, $p = 1$

Table on different settings: 
  (To show that we work comparably or better to EM always)

@@

Punchline: spectral by itself is medicore, offers a good initialization to EM.
EM with random initialization is much less stable.

@@

Plot the parameters: the curves, three algorithms

Plot: the histogram over errors

>>>>

Dataset 1: visualization ($b = 1, p = 3$) 
Plot for visualization

Table on different settings: 
  (To show that we work comparably or better to EM always)
  (Spawned!)

Dataset 2: $b = 30$, $p = 1$
(Spawned many tasks to find spec performance. Will run EM on interesting cases)

@@

Punchline: spectral by itself is medicore, offers a good initialization to EM.
EM with random initialization is much less stable. (by table)

@@

Plot the parameters: the curves, three algorithms (DONE)

Plot: the histogram over errors (for EM?)
